On Cybersecurity\\Science and Engineering\footnote{Confidential, restricted to the authors. Property of V-Research S.r.l.}

### 2020-06-01 reports/white_paper/abstract.tex
cybersecurity requirements improvements

The objective of this research is to develop of a theory that defines
(all and only) the possible insecurity and security configurations of
any abstract system. The theory is structured upon other theories that 
defines how a component of a system can be abstracted into an agent, defining how
agents can be formalized (both syntactically and semantically) to
describe an abstract system, such as a graph. Some of these theories
(e.g. used for the semantic
definition of the abstract system) are the epistemological definition
of knowledge, the Belief-Desire-Intent and the Assertion-Belief-Fact 
framework of reference, 
mereology, and topological structure. We argue that a mereology is the
most appropriate abstract underlying structure, due to its generality,
for defining the expressiveness of the system abstraction.  Furthermore, a
mereology allows us to define an ontology rather than a taxonomy.  We
also correlate different abstractions of the system to the TRL and the
engineering V-model.

We implemented a formal theory (of axioms) of a mereotopology, and of
the Region Connection Calculus (RCC3 and RCC5) in a Python program that
uses the Z3 SMT solver. The results show that a single component (i.e.
agent) of an abstract system has a definite number of  different
insecurity configurations (e.g. 53 using RCC5 over a topological
structure) and only 1 secure (i.e. expected) configurations. The
configurations are reported as models satisfying the abstract system
semantics.

We considered the philosophical definition of truth behind our
approach, rejecting ``proof'' by induction from partial empirical evidences.
Our theory can be applied to system engineering and we show a concrete
application of our theory to the risk assessment of an ad-hoc system.
Finally, we provide a number of ideas to support the engineering of
secure systems (e.g. purely cyber or cyber-physical).

>>>>

The objective of this research is the development of a theory that defines (all
and only) the possible insecurity and security configurations of any abstract
system. The theory is structured upon other theories that defines how a
component of a system can be abstracted into an agent, defining how agents can
be formalized (both syntactically and semantically) to describe an abstract
system, such as a graph. Some of these theories (e.g. used for the semantic
definition of the abstract system) are the epistemological definition of
knowledge, the Belief-Desire-Intent and the Assertion-Belief-Fact framework of
reference, mereology, and topological structure. We argue that a mereology is
the most appropriate abstract underlying structure, due to its generality, for
defining the expressiveness of the system abstraction.  Furthermore, a
mereology allows us to define an ontology rather than a taxonomy.  We also
correlate different abstractions of the system to the TRL and the engineering
V-model.

We implemented a formal theory (of axioms) of a mereotopology, and of the
Region Connection Calculus (RCC3 and RCC5) in a Python program that uses the Z3
SMT solver. The results show that a single component (i.e.  agent) of an
abstract system has a definite number of  different insecurity configurations
(e.g. 53 using RCC5 over a topological structure) and only 1 secure (i.e.
expected) configurations. The configurations are reported as models satisfying
the abstract system semantics. The implementation allows us to  apply our
theory to system engineering and showing concrete applications of our theory to
the risk assessment of an ad-hoc system.

### 2020-06-01 reports/white_paper/introduction.tex
cybersecurity requirements improvements

\epigraph{Humanum est errare}{{\itshape Seneca the Elder}}
The cybersecurity industry is growing fast (see Appendix~\ref{app:economy} for
a longer economic motivation), e.g. as reported in\autocite{Nasdaq2018market}.
For example, in\autocite{Forbes2017market}, published by the Forbes, is stated
that \euro5.3 billion of funding where poured by venture capitalist into
cybersecurity companies in 2018. The Forbes, in the same article, also
highlights another peculiar (as seemly contradictory) trend: ``[\ldots] during
the same time period, the number of cybersecurity breaches increased
exponentially''. The data reported by the NIST through the official CPE (Common
Platform Enumeration) Dictionary Statistics on the NVD websites in
\autocite{NIST2020CPEstatistics}, show that in 2016 the number of reported
vulnerabilities reported where around $~6000$ while in 2019 the number of
vulnerabilities was above $16000$.  The scientific community also reports
seemingly unjustifiable findings.  In fact, in\autocite{Herley2009so}, Cormac
Herley (Microsoft Research) shows how basic cybersecurity principles (such as
the confidentiality benefit over the clear text for passwords typed into forms,
e.g. for logins in websites) are not fully understood or shared between the
cybersecurity research community\autocite{Nielsen2009stop}.  The lack of
understanding of basic security principle, the inverse proportionality between
investments in cybersecurity and the number of reported vulnerabilities year
after year, can be linked to the lack of a foundational theory on
cybersecurity, as already highlighted by Cormac Herley
in\autocite{Herley2016unfalsifiability}.  An important issue raised by Herley
is that the methodology applied to by the security research community is quite
often implicit and not always scientifically ``correct''. Herley equates
correct to what Popper defined in \autocite{popper1962conjectures} even if, we
believe, the comments made by Hintikka in \autocite{Hintikka1993Information}
should be taken into account. Therefore, without discussing what correct and
non-correct is, we start by explicitly mention our method of enquiry.

\Paragraph{Methodology} The method applied in our line of research follows what
(to the best of our knowledge) the scientific method mandates. We start, in
Section~\ref{sec:problem}, by detailing the problem statement, reporting a
literature review on the main concepts and definitions related to security.  We
formulate (inductively)\footnote{``So, whenever they argue ``Every man is an
animal and Socrates is a man; therefore Socrates is an animal,'' proposing to
deduce from the universal proposition ``every man is an animal'' the particular
proposition ``Socrates therefore is an animal,'' which in fact goes (as we have
mentioned) to enstablish by way of induction the universal proposition, the
fall into the error of circular reasoning, since they are enstablishing the
universal proposition inductively by means of each of the particulars and
deducing the particular proposition from the universal syllogistically.''
Sextus Empiricus, Outlines of Pyrrhonism II-195
\autocite{Empiricus1990Pyrrhonism}} a security hypothesis, based on our review,
in Section~\ref{sec:glossary}; which we use to propose a theory on system security in
Section~\ref{sec:theory}. We apply our theory to an abstract and standard (i.e.
based on standards) secure process development lifecycle, following the
principle of requirement engineering in Section~\ref{sec:engineering} (with an
ad-hoc running example, based on the SWaT testbed \autocite{Mathur2016swat}).
We implement, in Section~\ref{sec:tool}, the theory in a prototype tool that can be used for the risk
assessment of a design of cyber-physical systems.

>>>>

\epigraph{Humanum est errare}{{\itshape Seneca the Elder}}
The cybersecurity industry is growing fast (see Appendix~\ref{app:economy} for
a longer economic motivation), e.g. as reported in\autocite{Nasdaq2018market}.
For example, in\autocite{Forbes2017market}, published by the Forbes, is stated
that \euro5.3 billion of funding where poured by venture capitalist into
cybersecurity companies in 2018. The Forbes, in the same article, also
highlights another peculiar (as seemly contradictory) trend: ``[\ldots] during
the same time period, the number of cybersecurity breaches increased
exponentially''. The data reported by the NIST through the official CPE (Common
Platform Enumeration) Dictionary Statistics on the NVD websites in
\autocite{NIST2020CPEstatistics}, show that in 2016 the number of reported
vulnerabilities were around $~6000$ while in 2019 the number of
vulnerabilities was above $16000$.  The scientific community also reports
seemingly unjustifiable findings.  In fact, in\autocite{Herley2009so}, Cormac
Herley (Microsoft Research) shows how basic cybersecurity principles (such as
the confidentiality benefit over the clear text for passwords typed into forms,
e.g. for logins in websites) are not fully understood or shared between the
cybersecurity research community\autocite{Nielsen2009stop}.  The lack of
understanding of basic security principle, the inverse proportionality between
investments in cybersecurity and the number of reported vulnerabilities year
after year, can be linked to the lack of a foundational theory on
cybersecurity, as already highlighted by Cormac Herley
in\autocite{Herley2016unfalsifiability}.  An important issue raised by Herley
is that the methodology applied by the security research community is quite
often implicit and not always scientifically ``correct''. Herley equates
correct to what Popper defined in \autocite{popper1962conjectures} even if, we
believe, the comments made by Hintikka in \autocite{Hintikka1993Information}
should be taken into account. Therefore, we start by explicitly mention our method of enquiry.

\Paragraph{Methodology} The method applied in our line of research follows what
(to the best of our knowledge) the scientific method mandates. We start, in
Section~\ref{sec:problem}, by detailing the problem statement, reporting a
literature review on the main concepts and definitions related to security.  We
formulate 
a security hypothesis %, based on our review,
in Section~\ref{sec:glossary}; which we use to propose a theory on system
security in Section~\ref{sec:theory}. In Section~\ref{sec:engineering}, we
apply our theory to an abstract and standard (i.e.  based on standards) secure
process development lifecycle, following the principle of requirement
engineering  (with an ad-hoc running example, based on the SWaT testbed
\autocite{Mathur2016swat}). This application shows how our theory can be used
to predict all of the possible security weaknesses of a system, allowing the
falsification of our theory.  In fact, if any security weaknesses were to be
found in a system and not predicted by our theory, the theory could be declared
incomplete.  Similarly, if a security weakness would be predicted by our theory
but found to be impossible to have our theory could be declared as wrong.  In
order to apply our theory we implemented, as described in
Section~\ref{sec:tool}, the theory in a prototype tool that can be used for the
risk assessment of a design of cyber-physical systems.
